\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-06-22 paper/main.tex
Updated via the Open Science Framework

@@

All experiments used the 2 $\times$ 2 design developed by \textcite{vandyke07}; the design crosses syntactic and semantic interference.

@@

Semantic interference is manipulated via the animacy of the distractor. During the retrieval of the subject of the verb \textit{trank} (`drank'), the animate distractor  \textit{Einbrecher} (`burglar') is assumed to cause high semantic interference, while the inanimate distractor \textit{Verlust} (`loss') is assumed to cause low semantic interference.

\paragraph{Regions of interest in the design}

Our principal focus was on the processing of the verb (\textit{trank}, `drank'). The reading times of the immediately following spill-over region and of the pre-critical region were also of interest. Previous work using the present design \parencite{vandyke07,mertzen} has consistently found effects in the pre-critical region (we return to this point in the discussion sections). A further issue with German embedded clauses \parencite[also see][]{mertzen} was that, without an appropriate intervening phrase, the clause embedding would lead to two verbs appearing one after another (\textit{erzählt hatte, trank}, literally `told, drank'). This is because in German, the verb is clause-final in embedded clauses. Such verb sequences are inherently difficult to process \parencite{VSLK11,bach1986crossed}.

@@

Thus, our focus in the present study is on the processing difficulty observed at the critical verb and the surrounding regions.

\subsubsection{Plausibility norming}
\citeauthor{vandyke07} conducted a pre-test to ensure that the distractor in high semantic interference conditions was a sufficiently probable subject of the critical verb, i.e., that it could potentially induce semantic interference. Following \citeauthor{vandyke07}, we also conducted a plausibility norming experiment.

@@

@@

In Experiment 1a, participants were re-invited for session 2 after they completed session 1. The experimental sessions were separated by 1 - 20 days. The procedure of the sessions was identical. Each session lasted approximately 25 minutes.

@@

The Bayes factor is analogous to the frequentist ANOVA or likelihood ratio test: it compares the marginal likelihood of a full model to that of a baseline null model; this is often written as $BF_{10}$, with the subscripts indicating that marginal likelihood of the full model is in the numerator and that of the null model is in the denominator. One major advantage of the Bayes factor over the frequentist analogue is that it takes the uncertainty of the parameters into account. This leads to more conservative inferences compared to frequentist ANOVA, which only takes the maximum likelihood estimate of the parameter into account \parencite[see][for detailed discussion]{schad_etal_2022_BF}. Another important advantage of the Bayes factor -- one that is very relevant for the present work -- is that it is possible to find evidence for or against an effect. This stands in contrast to the frequentist ANOVA which, in its standard usage, is designed to only furnish evidence against the null.

Bayes factors can be interpreted as follows \parencite[e.g., ][]{lee2014bayesian}: if BF$_{10}$ > 1, it provides evidence in favor of the effect of interest. If BF$_{10}$ < 1, it provides evidence in favor of the null model. The larger the value of BF$_{10}$, the stronger the evidence for the effect and the smaller the value of BF$_{10}$ is, the stronger the evidence for the null. 
In general, a large number of iterations is needed in the brms package in order to obtain stable estimates of the Bayes factor  \citep{schad_etal_2022_BF}.
For this reason, models were run with four chains and 20,000 iterations in each chain, with the first 2,000 iterations in each chain being discarded as the warm-up phase.  Bayes factors were unstable when varying slopes were included; for this reason, we fit the models only with varying intercepts by participant and by item.

@@

\subsubsection{Procedure}
The experiment was conducted in two experimental sessions for practical reasons (each of the sessions lasted approximately two hours). Sessions were separated by one to eight weeks for each participant (the median gap was two weeks, the first and third quartiles being one and three weeks). The procedure of both sessions was identical.

During each experimental session, the EEG was recorded while participants were
seated in a sound-proof booth. OpenSesame was used to present sentences word-by-word \citep{opensesame}. Participants were familiarized with the procedure with two practice sentences. After that, the experiment was conducted in four blocks of 50 sentences each, presenting the items in pseudorandomized order, with breaks between the blocks. Each trial started with the presentation of a fixation cross in the center of the screen for 500 ms. Next, each word of the sentence was presented in the center of the screen. Word duration for words of interest (subject, distractor, pre-pre-critical word, pre-critical word, critical verb, post-critical word) was 500 ms. Word duration of all other words was 190 ms + 20 ms per character of the specific word. The inter-stimulus interval between all words was 400 ms. After a third of the trials, participants were asked to answer yes/no comprehension questions by pressing one of two keys on a standard keyboard. The j key was always mapped to ``yes'' answers and the f key was always mapped to ``no'' answers. The correct response was counterbalanced, so that half of the time a ``no'' response was correct and half of the time a ``yes'' response was correct.

@@

We used Bayesian linear mixed models to analyze the single trial EEG data in response to the critical verb. We averaged the activity of 12 centro-parietal electrodes (Cz, C3/4, CPz, CP1/2, CP5/6, Pz, P3/4, POz) in the standard N400 time window (300 to 500 ms post critical word onset) for all analyses. The models included sum-contrast coded fixed effects for syntactic interference (high +0.5, low -0.5), semantic interference (high +0.5, low -0.5) and their interaction. In addition to the fixed effects of interest, all models included the baseline EEG activity from 200 ms prior to critical word onset until critical word onset as a continuous predictor. This functioned as a regression-based instead of traditional baseline correction \citep{alday2019}. Varying intercepts for participants and items as well as by-participant random slopes for semantic interference were included. Correlations between varying intercepts and slopes were not included. We used relatively informative priors for all parameters of the models (see Table \ref{tab:eeg_priors}).

\begin{table}[!htbp]
    \caption{Relatively informative priors for the analysis of the event-related potentials \citep{nicenboim_stats}. Priors on the slope parameters were truncated to an upper bound of zero, i.e., only negative values. This corresponds to more negative brain responses to high vs.\ low interference conditions in line with the literature \citep{lee_garnsey, martinetal2014, schoknecht2022, vasishth_drenhaus_2011}. The directional priors also serve to allow us to quantify the extent to which a predicted effect replicates; the Bayes factors can be interpreted as indicating the evidence supporting or not supporting replication success \citep{verhagen2014bayesian}.
    The standard deviations of the slope priors were varied in order to conduct a Bayes factor sensitivity analysis. See the corresponding assumed a priori range of the difference between high vs.\ low interference.}
    \label{tab:eeg_priors}
    \centering
    \begin{tabular}{lllr}
    \toprule
    Parameter&Prior & &Assumed Range ($\mu V$)\\
    \midrule
  Intercept & Normal(2, 5)& & [-8, 12]\\
  \cmidrule{2-4}
  \multirow{4}{1cm}{slope} & Normal(0, 0.1) &\hspace{-1em}\rdelim\}{4}{*}[upper bound: 0]& [-0.2, 0]\\
  & Normal(0, 0.5)& & [-1, 0]\\
  & Normal(0, 1) && [-2, 0]\\
  & Normal(0, 5) && [-11, 0]\\
  \cmidrule{2-4}
  sigma & Normal(10, 5)& \hspace{-1em}\rdelim\}{2}{*}[lower bound: 0]\\
  SD & Normal(0, 2)&\\
    \bottomrule
    \end{tabular}
\end{table}

@@

Figure \ref{fig:erp_all} shows the 
grand average ERPs elicited by the critical verb for all conditions. Table \ref{tab:eeg_mod} shows the estimates for the brain activity in the spatio-temporal N400 window from the linear mixed model with the truncated prior Normal$_-$(0, 0.5) which assumed more negative ERPs for high vs.\ low interference, with a difference possibly as large as -1\,$\mu V$. The 95\% credible intervals for the fixed effects are consistent with effects of syntactic interference, semantic interference and their interaction. The estimate of the semantic interference effect was the largest and its 95\% credible interval was the furthest from zero (mean: -0.31\,$\mu V$, 95\% CrI = [-0.49, -0.13]\,$\mu V$, for the posteriors, see Figure \ref{fig:eeg_posteriors}). The estimate of syntactic interference and the interaction were both about half the size of the semantic effect (see Table \ref{tab:eeg_mod} and Figure \ref{fig:eeg_posteriors}).

@@

\begin{table}[H]
    \caption{Results from the Bayesian linear mixed model analyzing the averaged brain response from 12 centro-parietal electrodes in the time window 300 to 500 ms post critical verb onset. The predictor baseline represents the averaged activity from the 200 ms pre-verb onset and was included in the model as a covariate instead of traditional baseline correction \citep[see][]{alday2019}.}
    \label{tab:eeg_mod}
    \centering
    \begin{tabular}{lrrr}
    \toprule
    & Estimate & Est.Error & 95\% CrI  \\
    \midrule
Intercept &  -0.70 & 0.19 &  [-1.06, -0.34] \\
baseline  &  -0.22 & 0.01 &  [-0.24, -0.20] \\
syntactic &  -0.15 & 0.08 &  [-0.32, -0.02] \\
semantic  &  -0.31 & 0.09 &  [-0.49, -0.13] \\
interaction& -0.13 & 0.10 &  [-0.37, -0.01] \\
    \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[H]
    \caption{Posteriors of the syntactic and semantic interference effects and their interaction for the event-related potentials elicited by the critical verb in the spatio-temporal N400 window. Blue vertical lines represent the median and shaded areas are 80\,\% intervals.}
    \label{fig:eeg_posteriors}
    \centering
    \includegraphics[width=0.6\textwidth]{images/posteriors_eeg.jpg}
\end{figure}

@@

Bayes factors are shown in Figure \ref{fig:eeg_bfs}. The Bayes factors provided very strong to strong evidence for the semantic interference effect for all priors 
(Normal$_{-}$(0, 0.1): BF$_{10}$ = 27,
Normal$_{-}$(0, 0.5): BF$_{10}$ = 88,
Normal$_{-}$(0, 1): BF$_{10}$ = 52,
Normal$_{-}$(0, 5): BF$_{10}$ = 11).

By contrast, the syntactic interference effect had only anecdotal evidence  under the two narrow priors (Normal$_{-}$(0, 0.1): BF$_{10}$ = 2.5,
Normal$_{-}$(0, 0.5): BF$_{10}$ = 1.2). There was evidence \textit{against} syntactic interference under wider priors 
(Normal$_{-}$(0, 1): BF$_{10}$ = 0.66,
Normal$_{-}$(0, 5): BF$_{10}$ = 0.14).  What this means is that, in our data, only if we assume a priori that the effect size is relatively small, there is very weak evidence in favor of syntactic interference.

@@

The Bayes factors analyses found strong evidence for semantic interference in the N400 amplitude. Syntactic interference had much weaker evidence in the N400 amplitude; only anecdotal evidence was found under narrow priors, and there was clear evidence against syntactic interference under wider priors. The evidence against an interaction under all priors was unequivocal.

@@

Consistent with the self-paced reading study, there is clear evidence for semantic interference, and evidence against syntactic interference.  How do these observed patterns compare to the theoretical predictions of cue-based retrieval theory? We turn to this point next by discussing the quantitative predictions of the \textcite{Lewis2005} model.

@@

\vspace{2em}
\section{Data availability statement}

The data and analysis scripts can be accessed via https://osf.io/4fpru/?view$\_$only=2d2a004d3e4147bc975b5e8c455c27df.

>>>>

\usepackage{clipboard}
\newclipboard{output-reviews}
\openclipboard{output-reviews}

@@

\Copy{vd_design}{All experiments used the 2 $\times$ 2 design developed by \textcite{vandyke07}; the design crosses syntactic and semantic interference.} \label{vd_design}

@@

Semantic interference is manipulated via the animacy of the distractor. During the retrieval of the subject of the verb \textit{trank} (`drank'), the animate distractor  \textit{Einbrecher} (`burglar') is assumed to cause high semantic interference, while the inanimate distractor \textit{Verlust} (`loss') is assumed to cause low semantic interference. \Copy{semantic_features_encoding}{\textcolor{blue}{The animacy of the distractor is used as a stand-in feature for semantic features relevant for the specific retrieval event which might be more fine-grained. In \ref{ex:materials}, the semantic retrieval cue might be \{+animate\} or \{+human\} but it might as well be \{+can drink\}. While more generic features like \{+animate\} or \{+human\} (all animate distractors were human) might be created during memory encoding, more specific features like \{+can drink\} are probably only activated when relevant. The present study is not designed to provide insight into the specific semantic features used during memory encoding and retrieval. A plausibility norming experiment (see page \pageref{plausib_normin_orig}) was conducted to ensure that the semantic manipulation did work, i.e., that the semantic requirements of the verb matched the features of the subject and the animate distractor, but not the features of the inanimate distractor.
}}\label{semantic_features_encoding}

\paragraph{Regions of interest in the design}
\textcolor{blue}{For both our SPR and EEG experiments, o}ur principal focus was on the processing of the verb (\textit{trank}, `drank'). \textcolor{blue}{In the SPR experiment, t}he reading times of the immediately following spill-over region and of the pre-critical region were also of interest. Previous work using the present design \parencite{vandyke07,mertzen} has consistently found effects in the pre-critical region (we return to this point in the discussion sections). A further issue with German embedded clauses \parencite[also see][]{mertzen} was that, without an appropriate intervening phrase, the clause embedding would lead to two verbs appearing one after another (\textit{erzählt hatte, trank}, literally `told, drank'). This is because in German, the verb is clause-final in embedded clauses. Such verb sequences are inherently difficult to process \parencite{VSLK11,bach1986crossed}.

@@

Thus, our focus in the \textcolor{blue}{SPR experiment} is on the processing difficulty observed at the critical verb and the surrounding regions.

\Copy{why_n400}{\textcolor{blue}{In the EEG experiment, the region of interest is the critical verb. Due to the direct measurement of brain activity with excellent temporal resolution event-related potential (ERP) effects do not tend to spill-over into later regions. We focus specifically on the N400 elicited by the verb. The N400 is a negative deflection in the ERP signal that peaks approximately 400 ms after any word was encountered. Traditionally, it is associated with lexical-semantic processing, but the finding of multi-modal N400 effects suggests that it rather indexes differences in the processing of meaningful stimuli in general \citep{kutas_federmeier2011}. The N400 amplitude is greater for words that deviate from the meaning activated by its context compared to words that fit its context \citep[see, e.g.,][]{kutas_hillyard, Kutas_Iragui_1998}. Consequently, the amplitude of the N400 to a specific word is a negative function of its predictability within the given context \citep{kutas_hillyard1984}. Additionally, the N400 elicited by isolated words is negatively correlated with their frequency \citep{kutas&federmeier_2000}. Therefore, the N400 amplitude is thought to index a) the increased difficulty to integrate a semantically anomalous or simply unexpected word into the sentence context \citep[e.g.,][]{hagoort2004integration} and/or b) the necessity to retrieve lexical information from memory which was not already pre-activated before the stimulus was perceived \citep[e.g.,][]{brouwer2017_n4_p6}. These two accounts of the N400 have been extensively discussed in the ERP literature on prediction \citep[see e.g.,][]{nieuwland_etal_2018, nicenboim_etal_2020, Freunberger_Roehm_2017, Delong_etal_2005, mantegna2019, nieuwland2019_integrationprediction}. As a likely marker of memory retrieval during sentence comprehension, it is fair to assume that the N400 would show modulations due to retrieval interference. The few ERP studies that have investigated retrieval interference so far have indeed found negativities \citep{lee_garnsey, martinetal2014, schoknecht2022, vasishth_drenhaus_2011}, although the topography and latency of these negativities was mostly not typical for the N400. It is important to highlight here that the previous ERP studies on interference either increased the number of distractors in a sentences or used grammatical gender or number as the critical retrieval cue. So, interference due to non-semantic features elicited negativities which were more or less similiar to the N400. Therefore, we expect the interference manipulation regardless of the type of retrieval cue (syntactic or semantic) to elicit N400 or similar effects. For a discussion of the relation between the N400 and other negativities, see \textcite{ina_n400}.}

\textcolor{blue}{Alternately, interference -- especially syntactic interference -- might modulate the P600. The P600 is a positive deflection in the ERP wave form that is typically observed at least 600 ms after stimulus onset. It is associated with syntactic processing, e.g., morpho-syntactic errors and reanalysis \citep[see, e.g.,][]{osterhout&holcomb_1992, kaan_etal_2000_P600}. High interference could increase difficulty during syntactic integration of subject and verb in our materials. Potential misretrievals of the distractor might lead to reanalysis processes which could manifest as an increased P600 amplitude compared to low interference conditions. To anticipate our results here, visual inspection of the ERPs in Figure \ref{fig:erp_syn_ERP} does not indicate syntactic interference effects in the P600 time window.}} \label{why_n400}

\subsubsection{Plausibility norming} \label{plausib_normin_orig}
\citeauthor{vandyke07} conducted a pre-test to ensure that the distractor in high semantic interference conditions was a sufficiently probable subject of the critical verb, i.e., that it could potentially induce semantic interference. Following \citeauthor{vandyke07}, we also conducted a plausibility norming experiment.

@@

\textcolor{red}{\section{Data availability statement}
All materials, data and analysis scripts can be accessed via https://osf.io/4fpru/?view$\_$only=2d2a004d3e4147bc975b5e8c455c27df.}\label{statement}

@@

\Copy{fillers1}{In Experiment 1a, participants were re-invited for session 2 after they completed session 1. The experimental sessions were separated by 1 - 20 days. The procedure of the sessions was identical. \textcolor{blue}{In session 1, the experimental items 1-60 were presented interspersed with 40 filler sentences. In session 2, the experimental items 61-120 were presented with another set of 40 filler sentences. The fillers were less syntactically complex than the experimental items but had at least one embedded clause and generally provided more variety (e.g., ``Der Teppichmacher, der früh in die Werkstatt gekommen war, reparierte den besonders schönen, alten Teppich während er die Nachrichten hörte'', `The carpet maker who came to the workshop early repaired the especially beautiful old carpet while listening to the news.'; ``Der Jugendliche war genervt, weil seine Freundin, die nicht studieren wollte, oft die Schule schwänzte, um Computer zu spielen.'', `The teenager was annoyed because his girlfriend who did not want to go to University  skipped school frequently to play video games.').}}\label{fillers1} Each session lasted approximately 25 minutes.

@@

\textcolor{blue}{Bayes factors were computed using the Savage-Dickey density ratio method. A Bayesian hypothesis test for which the posterior density is devided by the prior density at a specific parameter value of interest, e.g., zero \citep{wagenmakers_savagedickey, vuorre2017_savagedickey, dickey1970}.} The Bayes factor is often written as $BF_{10}$. \textcolor{blue}{To obtain $BF_{10}$ from the Savage-Dickey density ratio, we take its inverse.} One major advantage of the Bayes factor over \textcolor{blue}{frequentist ANOVA or likelihood ratio tests} is that it takes the uncertainty of the parameters into account. This leads to more conservative inferences compared to frequentist ANOVA, which only takes the maximum likelihood estimate of the parameter into account \parencite[see][for detailed discussion]{schad_etal_2022_BF}. Another important advantage of the Bayes factor -- one that is very relevant for the present work -- is that it is possible to find evidence for or against an effect. This stands in contrast to the frequentist ANOVA which, in its standard usage, is designed to only furnish evidence against the null.

Bayes factors can be interpreted as follows \parencite[e.g., ][]{lee2014bayesian}: if BF$_{10}$ > 1, it provides evidence in favor of the effect of interest. If BF$_{10}$ < 1, it provides evidence \textcolor{blue}{against the effect of interest}. The larger the value of BF$_{10}$, the stronger the evidence for the effect and the smaller the value of BF$_{10}$ is, the stronger the evidence \textcolor{blue}{against the effect of interest}. 
In general, a large number of iterations is needed in the brms package in order to obtain stable estimates of the Bayes factor  \citep{schad_etal_2022_BF}.
For this reason, models were run with four chains and 20,000 iterations in each chain, with the first 2,000 iterations in each chain being discarded as the warm-up phase.

@@

\subsubsection{Procedure}
The experiment was conducted in two experimental sessions for practical reasons (each of the sessions lasted approximately two hours). Sessions were separated by one to eight weeks for each participant (the median gap was two weeks, the first and third quartiles being one and three weeks). \Copy{fillers2}{The procedure of both sessions was identical \textcolor{blue}{and the same lists were used as in Experiment 1, with 60 critical sentences and 40 fillers per session}.

During each experimental session, the EEG was recorded while participants were seated in a sound-proof booth. OpenSesame was used to present sentences word-by-word \citep{opensesame}. Participants were familiarized with the procedure with two practice sentences. After that, the experiment was conducted in four blocks of \textcolor{blue}{25} sentences each, presenting the items in pseudorandomized order, with breaks between the blocks.}\label{fillers2} Each trial started with the presentation of a fixation cross in the center of the screen for 500 ms. Next, each word of the sentence was presented in the center of the screen. Word duration for words of interest (subject, distractor, pre-pre-critical word, pre-critical word, critical verb, post-critical word) was 500 ms. Word duration of all other words was 190 ms + 20 ms per character of the specific word. The inter-stimulus interval between all words was 400 ms. After a third of the trials, participants were asked to answer yes/no comprehension questions by pressing one of two keys on a standard keyboard. The j key was always mapped to ``yes'' answers and the f key was always mapped to ``no'' answers. The correct response was counterbalanced, so that half of the time a ``no'' response was correct and half of the time a ``yes'' response was correct.

@@

We used Bayesian linear mixed models to analyze the single trial EEG data in response to the critical verb. We averaged the activity of 12 centro-parietal electrodes (Cz, C3/4, CPz, CP1/2, CP5/6, Pz, P3/4, POz) in the standard N400 time window (300 to 500 ms post critical word onset) for all analyses. The models included sum-contrast coded fixed effects for syntactic interference (high +0.5, low -0.5), semantic interference (high +0.5, low -0.5) and their interaction. In addition to the fixed effects of interest, all models included the baseline EEG activity from 200 ms prior to critical word onset until critical word onset as a continuous predictor. This functioned as a regression-based instead of traditional baseline correction \citep{alday2019}. Varying intercepts for participants and items as well as by-participant \textcolor{blue}{and by-item} random slopes for \textcolor{blue}{syntactic interference,} semantic interference \textcolor{blue}{and their interaction} were included. We used relatively informative priors for all parameters of the models (see Table \ref{tab:eeg_priors}).

\begin{table}[!htbp]
    \caption{Relatively informative priors for the analysis of the event-related potentials \citep{nicenboim_stats}. Priors on the slope parameters were truncated to an upper bound of zero, i.e., only negative values. This corresponds to more negative brain responses to high vs.\ low interference conditions in line with the literature \citep{lee_garnsey, martinetal2014, schoknecht2022, vasishth_drenhaus_2011}. The directional priors also serve to allow us to quantify the extent to which a predicted effect replicates; the Bayes factors can be interpreted as indicating the evidence supporting or not supporting replication success \citep{verhagen2014bayesian}.
    The standard deviations of the slope priors were varied in order to conduct a Bayes factor sensitivity analysis. See the corresponding assumed a priori range of the difference between high vs.\ low interference.}
    \label{tab:eeg_priors}
    \centering
    \begin{tabular}{lllr}
    \toprule
    Parameter&Prior & &Assumed Range ($\mu V$)\\
    \midrule
  Intercept & Normal(2, 5)& & [-8, 12]\\
  \cmidrule{2-4}
  \multirow{4}{1cm}{slope} & Normal(0, 0.1) &\hspace{-1em}\rdelim\}{4}{*}[upper bound: 0]& [-0.2, 0]\\
  & Normal(0, 0.5)& & [-1, 0]\\
  & Normal(0, 1) && [-2, 0]\\
  & Normal(0, 5) && [-11, 0]\\
  \cmidrule{2-4}
  sigma & Normal(10, 5)& \hspace{-1em}\rdelim\}{2}{*}[lower bound: 0]\\
  SD & Normal(0, 2)&\\
 \textcolor{blue}{correlations} & \textcolor{blue}{LKJcorr(2)} & & \\
    \bottomrule
    \end{tabular}
\end{table}

@@

Figure \ref{fig:erp_all} shows the 
grand average ERPs elicited by the critical verb for all conditions. Table \ref{tab:eeg_mod} shows the estimates for the brain activity in the spatio-temporal N400 window from the linear mixed model with the truncated prior Normal$_-$(0, 0.5) which assumed more negative ERPs for high vs.\ low interference, with a difference possibly as large as -1\,$\mu V$. The 95\% credible intervals for the fixed effects are consistent with effects of syntactic interference, semantic interference and their interaction. The estimate of the semantic interference effect was the largest and its 95\% credible interval was the furthest from zero (\textcolor{blue}{mean: -0.32\,$\mu V$, 95\% CrI = [-0.59, -0.10]\,$\mu V$}, for the posteriors, see Figure \ref{fig:eeg_posteriors}). The estimates of syntactic interference and the interaction were both about half the size of the semantic effect (see Table \ref{tab:eeg_mod} and Figure \ref{fig:eeg_posteriors}).

@@

\begin{table}[H]
    \caption{Results from the Bayesian linear mixed model analyzing the averaged brain response from 12 centro-parietal electrodes in the time window 300 to 500 ms post critical verb onset. The predictor baseline represents the averaged activity from the 200 ms pre-verb onset and was included in the model as a covariate instead of traditional baseline correction \citep[see][]{alday2019}.}
    \label{tab:eeg_mod}
    \centering
    \begin{tabular}{lrrr}
    \toprule
    & Estimate & Est.Error & 95\% CrI  \\
    \midrule
Intercept &  -0.70 & 0.19 &  [-1.06, -0.34] \\
baseline  &  -0.22 & 0.01 &  [-0.24, -0.20] \\
syntactic &  \textcolor{blue}{-0.16}& \textcolor{blue}{0.08} &  \textcolor{blue}{[-0.33, -0.02]} \\
semantic  &  \textcolor{blue}{-0.30} & \textcolor{blue}{0.10} &  \textcolor{blue}{[-0.50, -0.11]} \\
interaction& \textcolor{blue}{-0.14} & \textcolor{blue}{0.11} &  \textcolor{blue}{[-0.40, -0.01]} \\
    \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[H]
    \caption{Posteriors of the syntactic and semantic interference effects and their interaction for the event-related potentials elicited by the critical verb in the spatio-temporal N400 window. Blue vertical lines represent the median and shaded areas are 80\,\% intervals.}
    \label{fig:eeg_posteriors}
    \centering
    \includegraphics[width=0.7\textwidth]{images/posteriors_eeg.jpg}
\end{figure}

@@

Bayes factors are shown in Figure \ref{fig:eeg_bfs}. The Bayes factors provided very strong to \textcolor{blue}{moderate} evidence for the semantic interference effect for all priors 
\textcolor{blue}{(Normal$_{-}$(0, 0.1): BF$_{10}$ = 11,
Normal$_{-}$(0, 0.5): BF$_{10}$ = 80,
Normal$_{-}$(0, 1): BF$_{10}$ = 9,
Normal$_{-}$(0, 5): BF$_{10}$ = 5)}.

By contrast, the syntactic interference effect had only anecdotal evidence  under the \textcolor{blue}{narrowest prior (Normal$_{-}$(0, 0.1): BF$_{10}$ = \textcolor{blue}{2.18}) and under the Normal$_{-}$(0, 0.5) prior there was no evidence for or against it (BF$_{10}$ = 1.05).} There was evidence \textit{against} syntactic interference under wider priors 
(Normal$_{-}$(0, 1): BF$_{10}$ = \textcolor{blue}{0.53},
Normal$_{-}$(0, 5): BF$_{10}$ = \textcolor{blue}{0.1}).  What this means is that, in our data, only if we assume a priori that the effect size is \textcolor{blue}{very small, i.e., maximally $-$0.2\,$\mu V$,} there is very weak evidence in favor of syntactic interference.

@@

The Bayes factors analyses found \textcolor{blue}{very strong to moderate evidence for semantic interference in the N400 amplitude for the whole range of investigated effects sizes ($-$0.2 to $-11$\,$\mu V$)}. Syntactic interference had much weaker evidence in the N400 amplitude; only anecdotal evidence was found under \textcolor{blue}{the narrowest prior, which assumed effect sizes smaller than $-$0.2\,$\mu V$. No evidence for or against syntactic interference was found under a prior which assumed a reasonable effect size of up to $-1$\,$\mu V$ ($BF_{10}$=1.05). There was clear evidence against syntactic interference under wider priors (effect sizes of up to $-$2 or up to $-11$\,$\mu V$)}. The evidence against an interaction under all priors was unequivocal. \textcolor{blue}{In sum, the ERP results showed clear evidence for semantic interference and clear evidence against an interaction of syntactic and semantic interference. The evidence for or against syntactic interference was dependent on the a priori assumed effect size. However, even when very small effects were assumed a priori, the evidence for syntactic interference was weak at best. Consequently, we conclude that the ERP data showed no syntactic interference.} \textcolor{red}{Add conclusion after SPR results are revised.}

@@

Consistent with the self-paced reading study, there is clear evidence for semantic interference, and \textcolor{blue}{little to no evidence for} syntactic interference.  How do these observed patterns compare to the theoretical predictions of cue-based retrieval theory? We turn to this point next by discussing the quantitative predictions of the \textcite{Lewis2005} model.

@@
